Screening harmonies

### 2020-07-16 choosing_harmonies.Rmd
choosing harmonies pdf update
add all ranking check

@@

>>>>

data_unite <- smart_chi %>% 
  left_join(smart_weibull, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
   rename("chisq" = "mean_max_variation.x", "weibull" = "mean_max_variation.y") %>% 
    left_join(smart_gamma,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>%  
  rename("gamma" = "mean_max_variation") %>% 
  left_join(smart_normal,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("normal" = "mean_max_variation") %>% 
   left_join(smart_general,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("general" = "mean_max_variation")

@@

```{r}
prob_plot(.data,  gran1 = "day_week", gran2 = "day_month", plot_type = "boxplot")

prob_plot(.data,  gran1 = "wknd_wday", gran2 = "day_month", plot_type = "boxplot")

prob_plot(.data,  gran1 = "wknd_wday", gran2 = "hour_day", plot_type = "boxplot")

### 2020-07-16 choosing_harmonies_Normal.Rmd
add all ranking check

One of the potential ways to evaluate this variation is by computing the pairwise distances between the distributions of the measured variable. We do this through Jensen-Shannon divergence which is based on Kullback-Leibler divergence. Probability distributions are represented through sample quantiles instead of kernel density estimate so that there is minimal dependency on selecting kernel or bandwidth.

@@

@@

# error after updating package and tsibble

<!-- ```{r cricket} -->
<!-- cricket_data <- read_rds("data/cricket_data.rds") -->

<!--   hierarchy_model <- tibble::tibble( -->
<!--       units = c("index", "over", "inning", "match"), -->
<!--       convert_fct = c(1, 20, 2, 1)) -->

<!-- hierarchy_tbl <- hierarchy_model -->

<!-- response <- "runs_per_over" -->

<!-- harmonies_cric <- cricket_data %>% harmony(lgran = "over", ugran = "match", filter_in = c("lag_field", "over"), hierarchy_tbl = hierarchy_model) -->
<!-- ``` -->

<!-- ```{r cricket_lag} -->
<!-- cricket_data <- read_rds("data/cricket_data.rds") -->
<!-- cricket_data %>% -->
<!--   filter(over!=1) %>% -->
<!--   prob_plot("over", "lag_field", -->
<!--   hierarchy_model, -->
<!--   response = "run_rate", -->
<!--   plot_type = "violin", -->
<!--   symmetric = FALSE, -->
<!--  quantile_prob = c(0.25, 0.5, 0.75)) + -->
<!--    #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") + -->
<!--   ylab("runs per over")  + -->
<!--   xlab("number of wickets in previous over") + -->
<!--   ggtitle("b") + -->
<!--    theme(plot.title = element_text(face = "bold")) +  theme_minimal() -->
<!-- ``` -->

@@

>>>>

One of the potential ways to evaluate this variation is by computing the pairwise distances between the distributions of the measured variable. We do this through Jensen-Shannon distance which is based on Kullback-Leibler divergence. Probability distributions are represented through sample quantiles instead of kernel density estimate so that there is minimal dependency on selecting kernel or bandwidth.

@@

```{r rank harmony}
library(gravitas)
library(ggplot2)
library(dplyr)
sm <- smart_meter10 %>%
filter(customer_id %in% c("10017936"))
harmonies <- sm %>%
harmony(ugran = "month",
filter_in = "wknd_wday",
filter_out = c("hhour", "fortnight"))
.data = sm
response  = "general_supply_kwh"
harmony_tbl =  harmonies
smart_harmony <- .data %>% rank_harmony(harmony_tbl = harmonies,
response = "general_supply_kwh", dist_ordered = FALSE)
```

@@

```{r cricket}
cricket_data <- read_rds("data/cricket_data.rds")

  hierarchy_model <- tibble::tibble(
      units = c("index", "over", "inning", "match"),
      convert_fct = c(1, 20, 2, 1))

hierarchy_tbl <- hierarchy_model

response <- "runs_per_over"

harmonies_cric <- cricket_data %>% harmony(lgran = "over", ugran = "match", filter_in = c("lag_field", "over"), hierarchy_tbl = hierarchy_model)
```

```{r cricket_lag}
cricket_data <- read_rds("data/cricket_data.rds")
cricket_data %>%
  filter(over!=1) %>%
  prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "violin",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("b") +
   theme(plot.title = element_text(face = "bold")) +  theme_minimal()
```

@@

```{r}
library(ggplot2)
library(gravitas)
sm <- smart_meter10 %>% dplyr::filter(customer_id %in% c("10017936"))

harmonies <- sm %>% 
  harmony(ugran = "month",
          filter_in = "wknd_wday",
          filter_out = c("hhour", "fortnight"))

.data = sm
response  = "general_supply_kwh"
harmony_tbl =  harmonies
smart_harmony <- .data %>% gravitas::rank_harmony(harmony_tbl = harmonies,
response = "general_supply_kwh", dist_ordered = FALSE)

smart_harmony %>% ggplot(aes(x = x_levels, y =  r)) + geom_point()
```
